---
title: "Analyse R Packages on Github"
author: "Michael Rustler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analyse R Packages on Github}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

is_travis_or_ghactions <- if (identical(Sys.getenv("TRAVIS"), "true") | identical(Sys.getenv("CI"), "true")) {
        TRUE } else { FALSE }
```


# Get Metadata for All KWB-R Github Repos

For all Github repos also includes non R packages

```{r, eval = TRUE}

  
pkgmeta::write_github_repos_json()


```


# Get Public KWB-R Github Package 

Now limit only "public" KWB-R repos which are R packages.

```{r, eval = TRUE}


pkgs <- pkgmeta::get_github_packages()


``` 





# Define paths 

```{r, eval = !is_travis_or_ghactions}
# Define paths and resolve placeholders

paths_list <- list(
  root_dir = tempdir(),
  pkglib = "<root_dir>/pkg-lib",
  pkgsource_dir = "<root_dir>/pkg-source",
  pkgnet_dir = "<root_dir>/pkgnet",
  pkgsource_zip_dir = "<pkgsource_dir>/zip",
  pkgsource_unzip_dir = "<pkgsource_dir>/unzip"
  )


paths <- kwb.utils::resolve(paths_list, root_dir = tempdir())

```


# Download dependencies

## Install Packages

in own library required for "codemetar" and "pkgnet" reports

```{r, echo = !is_travis_or_ghactions, eval = !is_travis_or_ghactions}


fs::dir_create(paths$pkglib, recursive = TRUE)

withr::with_libpaths(new = paths$pkglib,  {
  install.packages("remotes", repos = "https://cran.rstudio.org")  }
)

for(pkg in pkgs$name) {

withr::with_libpaths(new = paths$pkglib, {
  code = remotes::install_github(repo = sprintf("kwb-r/%s", pkg),
  dependencies = TRUE,
  upgrade = "always",
  auth_token =  Sys.getenv("GITHUB_PAT"))})
}

```
```{r, echo = is_travis_or_ghactions, eval = FALSE}
### On Travis already installed within .travis configuration
### https://github.com/KWB-R/pkgmeta/blob/master/.travis.yml
### with function 
pkgmeta::travis_pkg_install_script()
```





## Source Packages 

required for pkgnet "covr":

```{r, echo = !is_travis_or_ghactions, eval = !is_travis_or_ghactions}

fs::dir_create(path = c(paths$pkgsource_zip_dir, paths$pkgsource_unzip_dir), 
               recursive = TRUE)

for(pkg in pkgs$name) {
  pkgmeta::download_github(repo = sprintf("kwb-r/%s", pkg),
                           dest_dir = paths$pkgsource_zip_dir,
                           use_zip = TRUE,
                           auth_token = Sys.getenv("GITHUB_PAT"))
}
zipfiles <- list.files(paths$pkgsource_zip_dir,full.names = TRUE)

invisible(lapply(zipfiles, function(x) {
  message(glue::glue("Unzipping {x} to {paths$pkgsource_unzip_dir}"))
  unzip(x, exdir = paths$pkgsource_unzip_dir)}))

```



# Perform Package Meta Analysis

## With R package "codemetar"

Generating "codemetar.json" file

```{r, echo = !is_travis_or_ghactions, eval = !is_travis_or_ghactions}

pkgs <-  pkgmeta::get_github_packages()

codemeta <- pkgmeta::create_pkg_codemeta(pkgs, 
                                         libpath = paths$pkglib)


pkgmeta::write_pkg_codemeta_json(codemeta)
                                                     
```


```{r, echo=FALSE, eval = TRUE}

all_pkgs_installed <- all(pkgs$name %in% installed.packages()[,"Package"])

is_travis_and_all_pkgs_installed <-  is_travis_or_ghactions && all_pkgs_installed

```



```{r, echo = is_travis_or_ghactions, eval = is_travis_and_all_pkgs_installed}


pkgs_codemetar <-  pkgmeta::get_github_packages()

codemeta <- pkgmeta::create_pkg_codemeta(pkgs, 
                                         libpath = Sys.getenv("R_LIBS_USER"))



pkgmeta::write_pkg_codemeta_json(codemeta)

```


## With R package "pkgnet"

Create Reports with "pkgnet

```{r, echo = !is_travis_or_ghactions, eval = !is_travis_or_ghactions}
fs::dir_create(paths$pkgnet_dir, recursive = TRUE)

withr::with_libpaths(new = path$pkglib,
                     code = for(x in pkgs$name) {
   print(sprintf("Write report for R package: %s", x))
   pkg_src_unzipped <- dir(paths$pkgsource_unzip_dir, pattern = x)
   if(length(pkg_src_unzipped) > 1) {
      stop(glue::glue("Multiple unzipped pkg sources found in {paths$pkgsource_unzip_dir}:
                      {paste(pkg_src_unzipped, collapse = ', ')}.
                      Please delete the oldest one(s) manually"))
     #pkg_path <- file.path(paths$pkgsource_unzip_dir, pkg_src_unzipped),
     #sapply(pkg_path, function(x) {max(fs::dir_info(pkg_path[x])$modification_time)})
    } else if(length(pkg_src_unzipped) == 0)  {
      stop(glue::glue("No unzipped pkg sources found in {paths$pkgsource_unzip_dir}"))
    } else {
      try(pkgnet::CreatePackageReport(
         pkg_name = x,
         pkg_path = file.path(paths$pkgsource_unzip_dir, pkg_src_unzipped),
         report_path = file.path(paths$pkgnet_dir, paste0(x, ".html"))
        ))
  }})


```




